%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[sfdefault]{sourcesanspro}

\RequirePackage{tikz}
\usetikzlibrary{arrows}
\RequirePackage[skins]{tcolorbox}
\RequirePackage{enumitem}

\newcommand{\cvtag}[1]{%
  \tikz[baseline]\node[anchor=base,draw=body!30,rounded corners,inner xsep=1ex,inner ysep =0.75ex,text height=1.5ex,text depth=.25ex]{#1};
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape Rajath Chikkatur Srinivasa} \\ \vspace{1pt} \vspace
    {Atlanta, GA, USA}
    \small(470) 909-2758 $|$ \href{mailto:rajathcs.1996@gmail.com}{\underline{rajathcs.1996@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/rajathcs/}{\underline{linkedin.com/in/rajathcs/}} $|$
    \href{https://github.com/csrajath}{\underline{github.com/csrajath}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Georgia State University}{}
      {Graduate Teaching Assistant \& Research Member\href{http://www.panacealab.org/}{{-Panacea Lab}}}{Jan 2021 - Present}
      \resumeItemListStart
        \resumeItem{Used Git, Github \& Zenhub in for managing the student projects for Software Engineering course.}
        \resumeItem{Built python package, using NLP techniques like NER, to understand temporal data and performed \\ 
        sentiment analysis and visualization of tweets.}
      \resumeItemListEnd
    \resumeSubheading
      {Informatics Ltd.}{}
      {Product Developer}{Oct 2019 - Nov 2020}
      \resumeItemListStart
        \resumeItem{Utilized Linux JQ tool for processing large scale data and streamlined using {\textit{PySpark \& Azure Databricks.}}}
        \resumeItem{Built web scrapping bots, using {\textit{BeautifulSoup}} \& {\textit{PyPDF2}}, and scheduled it using {\textit{Apache Airflow}}}
        \resumeItem{Developed various components of admin module, using {\textit{Django \& React}}, for company's flagship product.}
    \resumeItemListEnd
    \resumeSubheading
      {K.P.M.G.}{}
      {Analyst}{Jun 2018 - Jun 2020}
      \resumeItemListStart
        \resumeItem{Queried Snowflake using SQL and Debugged 14, 000 lines of PL/SQL codebase.}        
        \resumeItem{Reviewed Python APIs used to built AWS infrastructure ({\textit{EC2, S3, CloudFormation, Lambda \& RDS}})}
      \resumeItemListEnd
      
    \resumeSubheading
      {Cell Propulsion Ltd.}{} 
      {Software Engineering Intern }{April 2018 - June 2018} 
      \resumeItemListStart
        \resumeItem{Designed and developed company’s \href{http://www.cellpropulsion.com/}{website} using HTMl, CSS, JavaScript and WordPress.}
        \resumeItem{Developed machine learning model to predict the correctness and health of sensor data in the autonomous driving system’s on-board computer. Leveraged Python and Shell scripting for building custom YOCTO packages that integrates the ML models.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{An Online QBE Processor for MySQL}}{}
          \resumeItemListStart
            \resumeItem{Implemented a Web-based QBE (Query By Example) Processor for MySQL databases. This processor will convert the visual query language into a MySQL query.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{A Framework for Building Inverted Index on Textual Data}}{}
          \resumeItemListStart
            \resumeItem{Built a scalable inverted index of Wikipedia corpus using {\textit {Hadoop \& MapReduce}}}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Parallel Mining of Frequent Itemsets in Real-Time Retail Dataset}}{}
          \resumeItemListStart
            \resumeItem{Created a web application that efficiently processes large scale retail transaction data using association mining algorithms. Performed automatic parallelization, load balancing and fault tolerance on a multi node-cluster.}
          \resumeItemListEnd       
      \resumeProjectHeading
          {\textbf{Automatic Extraction of Medication Names in Tweets}}{}
          \resumeItemListStart
            \resumeItem{Automatically extract \& classify medication names in tweets by training and testing data using {\textit {Random Forest, Logistic Regression, Naïve Bayes, SVM \& Perceptron}} models.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Dashboard for Real-Time visualization of Pedestrian Crashes}}{}
          \resumeItemListStart
            \resumeItem{Developed a Data Analytics tool for visually representation of the patterns observed for pedestrian-bicycle crashes and deployed on {\textit {Heroku}}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd    

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \cvtag {Python} \cvtag {Java}  \cvtag {SQL}   \cvtag {JavaScript} \cvtag {HTML} \cvtag {CSS} \cvtag {ReactJS} \cvtag {Django} \\
     \cvtag {Hadoop}  \cvtag {Spark} \cvtag {Tensorflow} \cvtag {AWS}  \cvtag {Azure} \cvtag {Jenkins} \cvtag {Docker} \cvtag {Git}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
    \resumeSubheading
      {M.S. - Computer Science}{}
      {Georgia State University, Atlanta}{Aug 2020 - Present}\newline
      
      {\footnotesize Algorithms, Data Science, Natural Language Processing}
      \resumeSubheading
      {B.E. - Information Science}{}
      {Don Bosco Institute of Technology, Bangalore}{Aug 2014 - May 2018}\newline
      
      {\footnotesize Data Structures, Web Programming, Software Engineering}
  \resumeSubHeadingListEnd
 
%-------------------------------------------
\end{document}
